Toxic Code Snippets on Stack Overflow

### 2018-11-27 cloverflow-tse/cloverflow.tex
Minor fixes to the paper: 1) Removed the name of Chris Bean -- GDPR 2) Corrected the number of GitHub projects to be the same as in the thesis 3) Updated the status of the Apache Hive issue (now closed)

Lastly, we searched for the outdated code snippets in 130,703 GitHub projects to
see how widespread is the outdated code in the wild. We mined GitHub
based on the number of stars the projects received, which indicated their popularity. We relied on
GitHub API to query the project metadata before cloning them.
Since GitHub API returned only top 1,000 projects at a time for each query, we formulated the
query to retrieve most starred projects based on their sizes.
The project size range started from 1KB to 2MB with 1KB step size, and the last query is
for all the remaining projects that were larger than 2MB.
With this method, we retrieved the top 1,000 most starred projects for each project size. 
As a result, we cloned 130,703 GitHub projects ranging from 29,465 stars to 1 star.
A clone detection was then performed between the outdated code snippets and the GitHub
projects. We selected SourcererCC with the same settings (see \Cref{tab:clone_config}) 
for this task because it could scale to a large-scale data set, while Simian could not. Finally, we analysed
the clone reports and manually checked the clones.

@@

We analysed code modifications which made Stack Overflow code outdated by going
through commits and git blame information. The six code modification
types found in the 100 outdated online clone pairs are summarised in
\Cref{tab:mod_types}. They include statement addition, statement modification,
statement removal, method rewriting, API change (changing in method signature),
and file deletion. We occasionally found multiple code modifications applied to
one clone pair at the same time but at a different location. The most often code
change found is statement modification (50 occurrences), followed by statement
addition (28 occurrences), statement removal (18 occurrences), change of
method signature, i.e.,~API change (16 occurrences), and method rewriting (15
occurrences). Moreover, in the 100 outdated pairs, we found 14 ``dead''
snippets. These snippets cannot be located in the latest version of the
projects. For example, the snippet in Stack Overflow post 3758110, a copy of
{\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in \textsf{spring}, was
deleted in the commit
{\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris Beams on
January 20, 2012, two years after it was posted.

@@

We performed a detailed investigation of the 100 outdated answers on Stack
Overflow, on 6 May 2018, approximately two years after the snapshot we analysed was created
to look for any changes, warnings, or mitigations made to the outdated code snippets.
We investigated the answers on three aspects: newer answers, higher-voted answers, and comments on the
outdated answers.\footnote{We also found that the Stack Overflow question ID 22262310 that has an outdated code answer from \texttt{WritableComparator.java} (\Cref{fig:before-after}), has a negative score of -1. It is interesting to see if the negative score for the question impacts both the number of views and the trust that people place in the answer to a down-voted question. However, it is out of the scope of this study so we leave it as future work.} We found
34 posts which contained newer answers and 5 posts which contained answers with a higher number of
votes than the outdated answers. However, 99 of the 100 outdated answers were still
marked as accepted answers. For the comments, we check if there is any comment
to mitigate or point out the toxicity of the outdated code snippets. We found
that, out of 100 answers, 6 answers had a comment saying the
code in the answer is outdated or containing issues, such as \textit{``spring
	3.1 stuff''}, \textit{``...tried this but having connect exception --
	\texttt{javax.mail.MessagingException}:\textit{ Could not connect to SMTP host:
	\texttt{smtp.gmail.com}, port: 465''}, ``You should add a \texttt{buffer.reset(null, 0, 0);} at the end of the try block to avoid excess heap usage (issue no. HADOOP-11323)''} or \textit{``.. I do not have experience
	with new versions of hibernate for a long time. But previously without clean you
	could receive some unexpected results. So I suggest to try different approaches
	or even check latest documentation''}. The 6 outdated code snippets were still
not fixed, but the comments themselves may help to warn some of the Stack Overflow
users.

@@

Then, we performed code clone detection between the 100 outdated code snippets and 130,703 GitHub projects.
We found 102 cloned candidates, which were associated with 30 outdated code snippets, 
appearing in 68 GitHub projects and manually investigated all
of them. Out of the 102 cloned snippets,
13 cloned snippets matched with themselves because some of the Qualitas
projects also appear on GitHub. For other projects besides the Qualitas
projects, 32 cloned snippets were not exactly the same
(e.g.,~they contained additional code modifications made by the projects'
developers, or they were copied from another source with a slightly different code).
47 cloned snippets were the same as the
outdated code snippets, which of 12 were buggy.
Two cloned snippets gave attributions to Stack Overflow. The attributions
pointed to different posts than the ones we found but containing the same code
in the answers\footnote{The answers were not marked as accepted so they were not 
included in our experiment.}. 32 cloned snippets were very likely to be a file-level
clone from its respective original project (e.g.,~JFreeChart, JUnit, Log4J,
Hadoop) based on their license header and the Javadoc comments. 
13 cloned snippets did not have any hints or evidence of copying.

Interestingly, we discovered that the buggy version of the
\texttt{humanReadableInt()} method from Hadoop appeared in two popular Java
projects: deeplearning4j (8,830 stars and 4,223 forks) and Apache Hive (1,854
stars and 1,946 forks). Due to the lack of evidence, we could not conclude how
this method, which is the same as the toxic code snippet we found on
Stack Overflow, appears in the two projects. It is possible that the developers
retrieved them from Stack Overflow, other websites, or from Hadoop code base
directly. Nevertheless, we reported them to the developers of the two projects
regarding the issue. We created a bug report for each project (deeplearning4j
\#4694\footnote{deeplearning4j bug report:
	\url{https://github.com/deeplearning4j/deeplearning4j/issues/4692}} and
HIVE-18929\footnote{Apache Hive bug report: \url{
		https://issues.apache.org/jira/browse/HIVE-18929}}) and communicated with the
developers of the projects by describing the problem of race condition in the
outdated version of the \texttt{humanReadableInt()} method and proposed a fix by
using the newest version of the method in Hadoop. The issue has been fixed in
deeplearning4j. The developers of deeplearning4j agreed that the method was
problematic and decided to implement their own fix due to a concern of a
potential software licensing conflict caused by copying the fix directly from
the Hadoop code base. The bug report in Apache Hive is still open.

@@

\begin{boxquote}
For RQ4, our results show that 66\% (101) of QS clone pairs on Stack
Overflow are outdated. 86 pairs differ from their newest versions by
modifications applied to variable names or method names, added or deleted
statements, to a fully rewritten code with new method signatures. 14~pairs are
dead snippets. 47 outdated code snippets are found in 130,703 GitHub projects
without evidence of copying, which of 12 were buggy. A toxic 
code snippet with a race condition was found in two popular projects: deeplearning4j and Apache Hive.
\end{boxquote}

@@

The same GitHub study has been done for license-incompatible code snippets. 
We detected clones between the 214
code snippets with their original license missing (86 QS, 78 EX, and 50 UD)  and
130,703 GitHub projects using SourcererCC with 80\% similarity threshold.
Opposite to the outdated clones, we discovered a large number
of 7,207 clone pairs. There were 95 pairs from 10 Qualitas projects hosted on
GitHub and 7,112 pairs from 2,427 other projects. As shown in
\Cref{tab:license_github}, the clones were found in highly-starred
projects (29,465 stars) to lowly-starred star projects (1 star).
We found 12 code snippets with attributions to Stack Overflow questions/answers and
6 of them refer to one of our QS or EX clone pairs.
We used the Ninka tool to identify software licenses of the 7,112 cloned
code snippets automatically. 
Five code snippets did not have a license while the originals had the Apache-2, GPLv2,
or EPLv1 license. One snippet had the AGPLv3 license while the original had the Apache-2 license.
Only 995 code snippets in GitHub projects have the same license
as the originals in Qualitas.

@@

We selected 130,703 GitHub Java projects
based on the number of stars they obtained to represent their popularity. They
might not represent all Java projects on GitHub, and the number of clone pairs
found may differ from other project selection criteria.

@@

We support the surveys' findings by performing a detailed analysis of toxic code
snippets on Stack Overflow. We investigated the online clone pairs on two
aspects: outdated code and potential license violation. The investigation of the
153 clone pairs copied, with evidence, from Qualitas to Stack Overflow reveals
that 100 of them are outdated. Twelve outdated clone pairs are buggy and toxic
to reuse. Our large-scale clone detection between the outdated code snippets 
and 130,703 GitHub projects finds 102 candidates of the outdated code being
used in the wild.
 Moreover, we found 214 code snippets on Stack Overflow that could
potentially violate the license of their original software, and they
occur in 7,112 times in 2,427 projects on GitHub.

>>>>

Lastly, we searched for the outdated code snippets in 130,719 GitHub projects to
see how widespread is the outdated code in the wild. We mined GitHub
based on the number of stars the projects received, which indicated their popularity. We relied on
GitHub API to query the project metadata before cloning them.
Since GitHub API returned only top 1,000 projects at a time for each query, we formulated the
query to retrieve most starred projects based on their sizes.
The project size range started from 1KB to 2MB with 1KB step size, and the last query is
for all the remaining projects that were larger than 2MB.
With this method, we retrieved the top 1,000 most starred projects for each project size. 
As a result, we cloned 130,719 GitHub projects ranging from 29,465 stars to 1 star.
A clone detection was then performed between the outdated code snippets and the GitHub
projects. We selected SourcererCC with the same settings (see \Cref{tab:clone_config}) 
for this task because it could scale to a large-scale data set, while Simian could not. Finally, we analysed
the clone reports and manually checked the clones.

@@

We analysed code modifications which made Stack Overflow code outdated by going
through commits and git blame information. The six code modification
types found in the 100 outdated online clone pairs are summarised in
\Cref{tab:mod_types}. They include statement addition, statement modification,
statement removal, method rewriting, API change (changing in method signature),
and file deletion. We occasionally found multiple code modifications applied to
one clone pair at the same time but at a different location. The most often code
change found is statement modification (50 occurrences), followed by statement
addition (28 occurrences), statement removal (18 occurrences), change of
method signature, i.e.,~API change (16 occurrences), and method rewriting (15
occurrences). Moreover, in the 100 outdated pairs, we found 14 ``dead''
snippets. These snippets cannot be located in the latest version of the
projects. For example, the snippet in Stack Overflow post 3758110, a copy of
{\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in \textsf{spring}, was
deleted in the commit
{\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} on
January 20, 2012, two years after it was posted.

@@

We performed a detailed investigation of the 100 outdated answers on Stack
Overflow, on May 6, 2018, approximately two years after the snapshot we analysed was created
to look for any changes, warnings, or mitigations made to the outdated code snippets.
We investigated the answers on three aspects: newer answers, higher-voted answers, and comments on the
outdated answers.\footnote{We also found that the Stack Overflow question ID 22262310, which has an outdated answer from \texttt{WritableComparator.java} (\Cref{fig:before-after}), has a negative score of -1. It is interesting to see if the negative score for the question impacts both the number of views and the trust that people place in the answer to a down-voted question. However, it is out of the scope of this study so we leave it as future work.} We found
34 posts which contained newer answers and 5 posts which contained answers with a higher number of
votes than the outdated answers. However, 99 of the 100 outdated answers were still
marked as accepted answers. For the comments, we check if there is any comment
to mitigate or point out the toxicity of the outdated code snippets. We found
that, out of 100 answers, 6 answers had a comment saying the
code in the answer is outdated or containing issues, such as \textit{``spring
	3.1 stuff''}, \textit{``...tried this but having connect exception --
	\texttt{javax.mail.MessagingException}:\textit{ Could not connect to SMTP host:
	\texttt{smtp.gmail.com}, port: 465''}, ``You should add a \texttt{buffer.reset(null, 0, 0);} at the end of the try block to avoid excess heap usage (issue no. HADOOP-11323)''} or \textit{``.. I do not have experience
	with new versions of hibernate for a long time. But previously without clean you
	could receive some unexpected results. So I suggest to try different approaches
	or even check latest documentation''}. The 6 outdated code snippets were still
not fixed, but the comments themselves may help to warn some of the Stack Overflow
users.

@@

Then, we performed code clone detection between the 100 outdated code snippets and 130,719 GitHub projects.
We found 102 cloned candidates, which were associated with 30 outdated code snippets, 
appearing in 68 GitHub projects and manually investigated all
of them. Out of the 102 cloned snippets,
13 cloned snippets matched with themselves because some of the Qualitas
projects also appear on GitHub. For other projects besides the Qualitas
projects, 32 cloned snippets were not exactly the same
(e.g.,~they contained additional code modifications made by the projects'
developers, or they were copied from another source with a slightly different code).
47 cloned snippets were the same as the
outdated code snippets, which of 12 were buggy.
Two cloned snippets gave attributions to Stack Overflow. The attributions
pointed to different posts than the ones we found but containing the same code
in the answers\footnote{The answers were not marked as accepted so they were not 
included in our experiment.}. 32 cloned snippets were very likely to be a file-level
clone from its respective original project (e.g.,~JFreeChart, JUnit, Log4J,
Hadoop) based on their license header and the Javadoc comments. 
13 cloned snippets did not have any hints or evidence of copying.

Interestingly, we discovered that the buggy version of the
\texttt{humanReadableInt()} method from Hadoop appeared in two popular Java
projects: deeplearning4j (8,830 stars and 4,223 forks) and Apache Hive (1,854
stars and 1,946 forks). Due to the lack of evidence, we could not conclude how
this method, which is the same as the toxic code snippet we found on
Stack Overflow, appears in the two projects. It is possible that the developers
retrieved them from Stack Overflow, other websites, or from Hadoop code base
directly. Nevertheless, we reported them to the developers of the two projects
regarding the issue. We created a bug report for each project (deeplearning4j
\#4694\footnote{deeplearning4j bug report:
	\url{https://github.com/deeplearning4j/deeplearning4j/issues/4692}} and
HIVE-18929\footnote{Apache Hive bug report: \url{
		https://issues.apache.org/jira/browse/HIVE-18929}}) and communicated with the
developers of the projects by describing the problem of race condition in the
outdated version of the \texttt{humanReadableInt()} method and proposed a fix by
using the newest version of the method in Hadoop. The issue has been fixed in both projects.
The developers of deeplearning4j agreed that the method was
problematic and decided to implement their own fix due to a concern of a
potential software licensing conflict caused by copying the fix directly from
the Hadoop code base. The developers of Apache Hive found that the method is not used anywhere
in the project, so they decided to delete it.

@@

\begin{boxquote}
For RQ4, our results show that 66\% (101) of QS clone pairs on Stack
Overflow are outdated. 86 pairs differ from their newest versions by
modifications applied to variable names or method names, added or deleted
statements, to a fully rewritten code with new method signatures. 14~pairs are
dead snippets. 47 outdated code snippets are found in 130,719 GitHub projects
without evidence of copying, which of 12 were buggy. A toxic 
code snippet with a race condition was found in two popular projects: deeplearning4j and Apache Hive.
\end{boxquote}

@@

The same GitHub study has been done for license-incompatible code snippets. 
We detected clones between the 214
code snippets with their original license missing (86 QS, 78 EX, and 50 UD)  and
130,719 GitHub projects using SourcererCC with 80\% similarity threshold.
Opposite to the outdated clones, we discovered a large number
of 7,207 clone pairs. There were 95 pairs from 10 Qualitas projects hosted on
GitHub and 7,112 pairs from 2,427 other projects. As shown in
\Cref{tab:license_github}, the clones were found in highly-starred
projects (29,465 stars) to lowly-starred star projects (1 star).
We found 12 code snippets with attributions to Stack Overflow questions/answers and
6 of them refer to one of our QS or EX clone pairs.
We used the Ninka tool to identify software licenses of the 7,112 cloned
code snippets automatically. 
Five code snippets did not have a license while the originals had the Apache-2, GPLv2,
or EPLv1 license. One snippet had the AGPLv3 license while the original had the Apache-2 license.
Only 995 code snippets in GitHub projects have the same license
as the originals in Qualitas.

@@

We selected 130,719 GitHub Java projects
based on the number of stars they obtained to represent their popularity. They
might not represent all Java projects on GitHub, and the number of clone pairs
found may differ from other project selection criteria.

@@

We support the surveys' findings by performing a detailed analysis of toxic code
snippets on Stack Overflow. We investigated the online clone pairs on two
aspects: outdated code and potential license violation. The investigation of the
153 clone pairs copied, with evidence, from Qualitas to Stack Overflow reveals
that 100 of them are outdated. Twelve outdated clone pairs are buggy and toxic
to reuse. Our large-scale clone detection between the outdated code snippets 
and 130,719 GitHub projects finds 102 candidates of the outdated code being
used in the wild.
 Moreover, we found 214 code snippets on Stack Overflow that could
potentially violate the license of their original software, and they
occur in 7,112 times in 2,427 projects on GitHub.
